Using simulation to optimize the sampling design of fisheries-independent trawl surveys

### 2018-08-30 analysis/presentation/sim_survey_presentation.Rmd
Add plot_ly based fan plot for true vs est comps

<dev class = "left">
<!-- There is a bug somewhere...had to contain plotly plots in a dev to get it working -->
```{r}
plot_trend(sim) %>% 
  tight_layout(margin = list(l = 70, r = 0, t = 0, b = 40, pad = 0))
```
</dev>

>>>>

<dev class = "left">
<!-- There is a bug somewhere...had to contain plotly plots in a dev to get it working -->
```{r}
plot_trend(sim) %>% 
  tight_layout(yaxis = list(rangemode = "tozero"),
               margin = list(l = 70, r = 0, t = 0, b = 40, pad = 0))
```
</dev>
